Site definition possibilites: Features excavated in a transect

### 2018-03-20 analysis/paper/paper.Rmd
commented the code some more.

# load data
## data cannot be provided, sorry. It is designed as a csv-file with the columns:
## Epoche -> epoch
## Abschnitt (früh | mittel | spät) -> period (early | middle | late)
## Kultur -> culture
## Befundart (Siedlung | Gräberfeld) -> kind of feature (settlement | grave)
## X -> coordinate
## Y -> coordinate

@@

library(dplyr)
table <- siedlung_BefSchnitt %>% group_by(epoche,abschnitt) %>% arrange(epoche,abschnitt) %>% summarise(count = n())

table2 <- siedlung_BefSchnitt %>% group_by(epoche, abschnitt, kultur) %>% arrange(epoche, abschnitt, kultur) %>% summarise(count = n())

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}

knitr::kable(table2[c(1, 3, 4)],
             col.names = c("Epoch", "Culture", "n settlement features"))

@@

#calculate distance matrix, create a vector and sort this vector
siedlSnK_dist_v <- sort(as.vector(pairdist.ppp(siedlung_SnK_Bef_pp)))
siedlSnK_dist_v <-subset(siedlSnK_dist_v, siedlSnK_dist_v > 0) # remove zeros
siedlSnK_dist_df <- as.data.frame(siedlSnK_dist_v) # create data frame

@@

# create complete spatial random point distribution

@@

siedlSnK_dist_df_1000$n <-c(1:nrow(siedlSnK_dist_df_1000)) # as the vector has been sorted, the row gives the number how many have this or a smaller distance
siedlSnK_dist_df_1000$prozent <-c(siedlSnK_dist_df_1000$n/nrow(siedlSnK_dist_df_1000)) # creates a proportion for comparison

@@

>>>>

# load data
## data cannot be provided, sorry. It is designed as a csv-file with the columns:
## Epoche (Neolithikum | Bronzezeit | Eisenzeit | undatiert) -> epoch (Neolithic | Bronze Age | Iron Age | not dated)
## Abschnitt (früh | mittel | spät) -> period (early | middle | late)
## Kultur -> culture
## Befundart (Siedlung | Gräberfeld) -> kind of feature (settlement | grave)
## X -> coordinate
## Y -> coordinate

@@

library(dplyr)
# calculate number and percentages of features by epoch and period
table <- siedlung_BefSchnitt %>% group_by(epoche,abschnitt) %>% arrange(epoche,abschnitt) %>% summarise(count = n())

# calculate number and percentages of features by epoch and period and culture
table2 <- siedlung_BefSchnitt %>% group_by(epoche, abschnitt, kultur) %>% arrange(epoche, abschnitt, kultur) %>% summarise(count = n())

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
# create nice readable table
knitr::kable(table2[c(1, 3, 4)],
             col.names = c("Epoch", "Culture", "n settlement features"))

@@

#calculate distance matrix, create a vector and sort this vector for different cultures
siedlSnK_dist_v <- sort(as.vector(pairdist.ppp(siedlung_SnK_Bef_pp)))
siedlSnK_dist_v <-subset(siedlSnK_dist_v, siedlSnK_dist_v > 0) # remove zeros
siedlSnK_dist_df <- as.data.frame(siedlSnK_dist_v) # create data frame

@@

# create complete spatial random point distribution for comparison

@@

siedlSnK_dist_df_1000$n <-c(1:nrow(siedlSnK_dist_df_1000)) # as the vector has been sorted, the row gives the number how many have this or a smaller distance
siedlSnK_dist_df_1000$prozent <-c(siedlSnK_dist_df_1000$n/nrow(siedlSnK_dist_df_1000)) # creates a proportion for comparison
# repeat for all other cultures:

@@

# plot KDE on top of distance vectors. Silverman's Rule of Thumb is bandwidth
